\section{Related Work}
\label{sec:related}

\paragraph{Universal adversarial attacks on multimodal LLMs.}
The Universal Adversarial Attack (UAA) of \citet{rahmatullaev2025universal} optimises a single image that, when paired with any of $60$ benign prompts, drives an aligned multimodal LLM toward a chosen target phrase. They report jailbreak ASR up to $81\%$ on SafeBench / MM-SafetyBench. Earlier, \citet{schlarmann2023robustness} showed that perturbations as small as $\eps=1/255$ can re-route VLM captions to attacker-chosen URLs, and \citet{qi2024visual} demonstrated that one visual adversarial example can universally jailbreak aligned VLMs into following harmful instructions outside the optimisation corpus. \citet{carlini2024aligned} further established that multimodal models are roughly an order of magnitude easier to break than their text-only counterparts. \citet{bailey2024image} introduced ``image hijacks'' --- behaviour-matching adversarial images for output-control, context-exfiltration, safety-override, and false-belief attacks --- with ASR $\geq 80\%$ against LLaVA \citep{liu2023llava}. We build on \citet{rahmatullaev2025universal} directly: their PGD optimisation is our Stage~1 (\S\ref{sec:method-stage1}). Our contribution relative to these works is the post-fusion dual-axis evaluation, which separates the broad-but-shallow disruption their methods deliver from the rare-but-targeted payload delivery they sometimes claim.

\paragraph{AnyAttack and CLIP-based fusion.}
\citet{zhang2025anyattack} train a self-supervised CLIP-encoder + decoder pair on bidirectional COCO that maps any image's CLIP feature to an \Linf{}-bounded noise tensor. The decoder is general-purpose: it produces transferable adversarial perturbations against frontier closed VLMs without per-target retraining. We reuse the public \texttt{coco\_bi.pt} weights as our Stage~2 (\S\ref{sec:method-stage2}), feeding it the Stage-1 universal image rather than a CLIP target embedding.

\paragraph{Indirect prompt injection.}
\citet{greshake2023indirect} (AISec'23) introduced the indirect-prompt-injection (IPI) taxonomy --- attacks that smuggle instructions through retrieved data or third-party documents rather than directly through the user prompt. \citet{bagdasaryan2023imagessounds} ported this idea to images and audio, demonstrating adversarial perturbations that act as instruction injections against LLaVA and PandaGPT. \citet{liu2024formalizing} (USENIX Security 2024) provide a formal definition --- a successful injection requires the target string to appear in the response --- which we adopt as the basis of our Target Injected check. Our work is the visual-modality analogue of these benchmarks, with explicit dual-axis scoring.

\paragraph{Multimodal jailbreaks against aligned VLMs.}
\citet{zou2023gcg} introduced GCG --- a transferable suffix attack on aligned LLMs that became the textual analogue of universal visual attacks. The visual branch has produced a growing list of methods: \textsc{Jailbreak-in-Pieces} \citep{shayegani2024jailbreak} (ICLR 2024 Spotlight) splits the payload across image and text modalities; \textsc{FigStep} \citep{gong2025figstep} (AAAI 2025 Oral) renders prohibited text typographically and reports $82.5\%$ ASR average across six open VLMs; \textsc{HADES} \citep{li2024hades} (ECCV 2024 Oral) combines typography with diffusion-generated harmful imagery and adversarial perturbation, hitting $90.3\%$ ASR on LLaVA-1.5 and $71.6\%$ on Gemini Pro Vision. We differ from this family in threat model: we attack \emph{output integrity} under \emph{benign user prompts}, whereas these works attack safety alignment under adversarial prompts. The high-ASR numbers in this literature partly motivate our methodological critique --- they measure ``safety failure,'' not ``payload delivery,'' and the two are not the same.

\paragraph{Foundational adversarial-attack methodology.}
The optimisation primitives we use trace back to \citet{goodfellow2015explaining} (FGSM, the original gradient-based image attack), \citet{madry2018pgd} (PGD adversarial training, which we use without modification as our Stage-1 inner loop), and \citet{moosavi2017uap} (the original ``universal'' framing --- a single perturbation that fools many inputs). Defense work in this space (\textsc{Robust CLIP} \citep{schlarmann2024robustclip}, \textsc{VLGuard} \citep{zong2024vlguard}, \textsc{ECSO} \citep{gou2024ecso}, etc.) is orthogonal to our methodology contribution and not benchmarked here; we do not propose a defense in this paper. \S\ref{sec:discussion} discusses which classes of defense our findings predict would be effective.

\paragraph{Evaluation methodology and benchmarks.}
\textsc{HarmBench} \citep{mazeika2024harmbench} (ICML 2024) standardises evaluation across $18$ attacks $\times$ $33$ LLM/defenses with four behaviour categories. \textsc{JailbreakBench} \citep{chao2024jailbreakbench} (NeurIPS 2024 D\&B) provides an open evolving repo of $100$ behaviours with leaderboard scoring. \textsc{MM-SafetyBench} \citep{liu2024mmsafetybench} (ECCV 2024) extends to the multimodal setting with $5{,}040$ image-text pairs across $13$ unsafe scenarios. None of these benchmarks separate Influence from Precise Injection; their scoring is a single Boolean ``did the model produce harmful / target content'' typically judged by an LLM-as-judge \citep{zheng2023judge}. Our contribution is to expose this gap by reporting both axes explicitly across $6{,}615$ pairs --- we find roughly a $90\times$ divergence on the same data ($66.4\%$ programmatic disruption vs $0.756\%$ broad injection by the v3 LLM judge). The released dataset (\S\ref{sec:conclusion}) is intended to slot into HarmBench / JailbreakBench-style regression suites with both axes available per pair.
