\section{Conclusion}
\label{sec:conclusion}

We composed two existing universal-attack methods --- the Universal Adversarial Attack of \citet{rahmatullaev2025universal} and the \textsc{AnyAttack} encoder--decoder of \citet{zhang2025anyattack} --- with a dual-axis LLM-judged evaluation that scores Influence (drift) and Precise Injection (payload delivery) independently. Each pair is judged by \textsc{DeepSeek-V4-Pro} \citep{deepseekv3} in thinking mode, calibrated against Claude Opus 4.7 \citep{anthropic2025opus47} with Cohen's $\kappa = 0.77$ on the injection axis (substantial agreement, \citealp{landiskoch1977}); a deterministic Ratcliff-Obershelp baseline is reported alongside. Across $6{,}615$ (clean, adversarial) response pairs over four open \vlm{}s, seven attack prompts, and seven test images at $\Linf = 16/255$ and PSNR $\approx 25.2$~dB, programmatic disruption ($66.4\%$) and LLM-judged disruption ($46.6\%$ at the substantial+complete tiers) coexist with rare verbatim injection ($0.030\%$, $2/6{,}615$) and modest broad injection ($0.756\%$, $50/6{,}615$ when theme-fragments are counted) --- a roughly $90\times$ divergence on the same data, with the tier decomposition discussed in \S\ref{sec:results} and Appendix~\ref{app:variants}. The full LLM-call cache is shipped with the dataset so any reviewer can replay paper numbers bit-exact without an API key. The few injections that do land cluster on screenshot- or document-style images whose semantic class matches the payload's category; a single-case manual transfer test against GPT-4o (suggestive, not a systematic measurement) fails; BLIP-2 shows zero detectable drift at $\Linf = 16/255$ across every pair we evaluate, even when used as a Stage-1 surrogate.

Two implications stand out. First, single-number ``ASR'' metrics in the universal-attack-on-VLM literature conflate disruption with payload delivery, and the two diverge by orders of magnitude. Future evaluations should report both axes. Second, the BLIP-2 result suggests that information-bottleneck architectures (Q-Former-style) may already provide substantial adversarial robustness against \eps{}-bounded attacks at no additional training cost --- a defense direction that does not require expensive adversarial fine-tuning of the vision encoder.

\paragraph{Future work.}
Three natural extensions are out of scope here. (i) A direct $x_u \to$ BLIP-2 ablation (skipping Stage 2 fusion) would distinguish whether the immunity sits in the AnyAttack decoder or in BLIP-2's architecture itself. (ii) A systematic transferability study across multiple frontier closed models (ChatGPT, Gemini, Claude) on multiple cases would replace this paper's single GPT-4o anecdote with a measured rate. (iii) Extending the attack family beyond gradient-based pixel perturbation (typographic injection, steganographic embedding, scene spoofing) would test whether the disruption-versus-injection gap holds across the wider visual-injection design space.

\paragraph{Reproducibility.}
Both attack stages use public pretrained weights without retraining (\texttt{coco\_bi.pt} for AnyAttack); the dual-axis judge invokes DeepSeek-V4-Pro per pair, but the entire $4{,}475$-entry SHA-256 input cache is shipped with the dataset, so the canonical reproduction path is \texttt{python -m evaluate.replay --cache judge\_cache.json --pairs-dir experiments/}, which runs in $\sim 30$ seconds on a laptop CPU and reproduces every paper number bit-exact \emph{without} an API key. A reviewer who prefers to call the API independently can re-run \texttt{evaluate.judge}; agreement to within $\sim 5\%$ at the per-pair level is expected, since DeepSeek does not currently expose a deterministic \texttt{seed} parameter. Stage~1 takes $7$--$19$ minutes per universal image on a single H200 80~GB; Stage~3a generation is the dominant wall-clock cost ($\sim 30$ minutes per (image, experiment) row). Hyperparameters: PGD steps $= 2{,}000$, learning rate $10^{-2}$ (Adam), $\eps = 16/255$, ensemble sizes $N \in \{2, 3, 4\}$.

\paragraph{Released artifacts.}
\begin{itemize}
  \item Dataset (CC-BY-4.0): \url{huggingface.co/datasets/jeffliulab/visinject} --- $21$ universal adversarial images, $147$ adversarial photos, $6{,}615$ response pairs with v3 dual-axis judge scores, the $4{,}475$-entry \texttt{judge\_cache.json} for cache-replay reproducibility, an \texttt{evaluator\_manifest.json} pinning model snapshot + rubric SHA-256 + calibration $\kappa$, the $100$-pair calibration set with both human and DeepSeek labels, and $12$ image files (4 clean + 8 adversarial) covering the $10$ curated injection case studies (\S\ref{sec:cases}).
  \item Code (MIT license): \url{github.com/jeffliulab/vis-inject} --- full pipeline, all VLM wrappers, and the dual-axis judge. The exact code state used in this paper is preserved at git tag \texttt{v1.5}.
  \item Demo Space (CPU-only, free tier): \url{huggingface.co/spaces/jeffliulab/visinject} --- pick an attack prompt, see the corresponding Stage-1 universal abstract image, upload any clean photo, and download the Stage-2 adversarial output.
\end{itemize}

\paragraph{Paper licence.}
This paper is released under the Creative Commons Attribution 4.0 International licence (CC-BY-4.0), matching the dataset.

\paragraph{Acknowledgments.}
The first author thanks his Tufts Electrical \& Computer Engineering coursework for providing the initial scope, and the corresponding author for guidance and for handling the arXiv submission process. Writing assistance, including iterative editing of the LaTeX source and the dual-axis judge implementation, was provided in part by the Anthropic Claude AI assistant; all empirical results, dataset construction, and final claims are the authors' responsibility.
